\documentstyle[12pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-.3in}
\setlength{\textheight}{9in}
\pagestyle{empty}



\newcommand{\university}{University of Minnesota }
\newcommand{\uni}{UMN }



\begin{document}

\begin{center}
{\Large \huge \scshape Personal Statement (DRAFT \#1)} \\[.3in]
{\large Adam R. Stammer}
\end{center}

\vspace*{.1in}

When I was 6 years old I remember getting back from the grocery store. My three older sisters and I grabbed some groceries to bring inside, and our father dropped the gallon of milk spilling it across the sidewalk in seconds. We all knew that gallon had to last us two weeks, and I could see my dad trying to hide the fact that he was crying. I know that sounds like a bad joke, but I can assure you that eating generic cornflakes in water wasn't funny for long. I always knew we were poor, but it wasn't until that experience that I began to truly understand. This was when I first started to think about going to college, though I didn't yet know what that really meant.

Going to middle school just a block from my house, I found myself a racial minority in most classes. I never judged a person by the color of their skin, or where they came from, but I was discouraged to find my story was not at all uncommon. Many of my peers had less than even I did. Some of my friends ate more at school than they ever did at home thanks to need-based financial assistance toward school meals. This combined with the perspective I gained from my sisters exposed me to many of the systemic inequalities, in a way that words never could. My father worked well over 40 hours a week, at multiple jobs, while raising 4 children. He made sacrifices nobody should have to make to provide his family with basic necessities. So many people out there sacrifice so much more for even less. These early experiences narrowed my purpose and steeled my resolve to make a lasting impact.

Around the same time, one of my friends introduced me to batch programming and encouraged me to learn too. I didn't have internet at home, so I would walk to my grandparents house and use their internet to research programming languages and worked on projects with my friend. By the end of middle school we had become familiar with over 3 major programming languages and were both considering Computer Science as a future career field. My most influential project was born out of our desire to learn Python. We were testing out a new animation API and decided to make our own Pong game. It was so many new things for us including networking, applying trigonometry and algebra that we had just learned in school, and manual filestreams, and we communicated the design entirely by voice alone. We were so proud of the end product and couldn't stop playing, so I tweaked some of the code to allow my paddle to go any direction as a prank on my friend. It proved to myself that I understood what we had built. That project showed me that I could learn and build anything I set my mind to, and that I loved to do it! It also taught me that I didn't have to do it alone. 

[a paragraph about the research project I'm working on, or a story about how sustainability has become a primary motivator of mine]

\end{document}
